README

### 2020-04-03 simulation_study/simulation/README.Rmd
add config file LCTD all

```{r}
# get config files
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
# manually transform
# push to github

sims[condition[8], d, "one"] <- 1 # simulation configs are up
# run simulations

scdd <- createLines(condition[8], d, "one")

sims[condition[8], d, "one"] <- 2 # simulations are running 
# transfer to harddrive 
transfer()
sims[condition[8], , "one"] <- 3 # output is on harddrive
```

@@

```{r template, eval = FALSE}
# get config files
scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config /Volumes/Gerbrich/asreview/config/optimization_output
# manually transform
# push to github 
sims[condition[1], d, "one"] <- 1 # simulation configs are up
# run simulations 
createLines()
sims[condition[1], d, "one"] <- 2 # simulations are running 
# transfer to harddrive 
transfer()
sims[condition[1], , "one"] <- 3 # output is on harddrive
```

>>>>

```{r}
# get config files
# manually transform
# push to github 
sims[condition[8], d, "one"] <- 1 # simulation configs are up

# run simulations 
scdd <- createLines(condition[8], d, "one")
write.table(scdd, file = "scripts/one/scdd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(scdd) <- c("7893237", "7893241", "7893243", "7893244", "7893246", "7893247")
sims[condition[8], d, "one"] <- 2 # simulations are running

# transfer to harddrive 
transfer("hp", condition[8])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

all - LCTD hyperparameters 
```{r}
# manually transform
# push to github 
sims[condition[4], , "all"] <- 1 # configs are on github 
```

@@

```{r template, eval = FALSE}
# get config files
# manually transform
# push to github 
sims[condition[1], d, "one"] <- 1 # simulation configs are up
# run simulations 
createLines()
sims[condition[1], d, "one"] <- 2 # simulations are running 
# transfer to harddrive 
transfer()
sims[condition[1], , "one"] <- 3 # output is on harddrive
```
